### 2015-06-01 writing/SNLI paper/corpus.tex
CP comments.

To date, the primary sources of annotated NLI corpora have been the
Recognizing Textual Entailment (RTE)
challenge tasks.\footnote{\url{http://aclweb.org/aclwiki/index.php?title=Textual_Entailment_Resource_Pool}}
These are generally high-quality, hand-labeled data sets, and they
have stimulated innovative logical and statistical models of natural
language reasoning, but their small size (fewer than a thousand examples each)
limits their utility as a testbed for learned distributed representations. 
The data for the SemEval 2014 task called Sentences Involving Compositional Knowledge (SICK) is a
step up in terms of size, but only to 4,500 training examples, and its
partly automatic construction introduced some spurious patterns into
the data (\citealt{marelli2014semeval}, $\S$6). Finally, the
Denotation Graph entailment set \cite{hodoshimage} contains millions of
examples of entailments between sentences and artificially constructed
short phrases, but it was labeled using fully automatic methods, and is
noisy enough that it is probably suitable only as a source of
supplementary training data. The Paraphase Database of \citealt{ganitkevitch2013ppdb}
addresses these issues of size and quality, but only for the limited
fragment of the NLI problem that is captured by paraphase.

@@

With our corpus, we sought to address the issues of size, quality, and
indeterminacy. To do this, we employed a crowdsourcing framework with
the following crucial innovations. First, the examples were grounded
in specific scenarios, and the premise and hypothesis sentences in each example 
are constrained to describe that scenario from the same perspective, 
which helps greatly in controlling event and entity coreference. Second, the prompt
gave participants the freedom to produce entirely novel sentences
within the task setting, which led to richer examples than we see with
the more proscribed string-editing techniques of earlier approaches,
without sacrificing consistency. Third, a subset of the resulting
sentences were sent to a validation task aimed at providing highly reliable set of annotations over the same data, and at identifying areas of inferential uncertainty.

@@

In order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we performed an additional round of validation for about 10\% of our data.
This validation phase followed the same basic form as the Mechanical Turk labeling task used to label the SICK entailment data: we presented workers with pairs of sentences in batches of five, and ask them to choose a single label for each pair. We supplied each pair to four annotators, yielding five labels per pair including the label used by the original author. The instructions were similar to the instructions for initial data collection shown in \reffig{instructions-1}, and linked to a similar FAQ. Though we initially used a very restrictive qualification (based on past approval rate) to select workers for the validation task, we nonetheless discovered (and excluded from the corpus) some instances of random guessing in an early batch of work, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.

@@

The results of this validation process
are summarized in \reftab{validation-stats}. 
Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing. The Fleiss $\kappa$ scores 
(computed over every example with a full five annotations)
are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rate of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

The data will be released upon publication under a CreativeCommons
Attribution-ShareAlike licence, the same licence used for the Flickr30k source captions.

>>>>

To date, the primary sources of annotated NLI corpora have been the
Recognizing Textual Entailment (RTE)
challenge tasks.\footnote{\url{http://aclweb.org/aclwiki/index.php?title=Textual_Entailment_Resource_Pool}}
These are generally high-quality, hand-labeled data sets, and they
have stimulated innovative logical and statistical models of natural
language reasoning, but their small size (fewer than a thousand examples each)
limits their utility as a testbed for learned distributed representations. 
The data for the SemEval 2014 task called Sentences Involving Compositional Knowledge (SICK) is a
step up in terms of size, but only to 4,500 training examples, and its
partly automatic construction introduced some spurious patterns into
the data (\citealt{marelli2014semeval}, $\S$6). Finally, the
Denotation Graph entailment set \cite{hodoshimage} contains millions of
examples of entailments between sentences and artificially constructed
short phrases, but it was labeled using fully automatic methods, and is
noisy enough that it is probably suitable only as a source of
supplementary training data. The Paraphase Database of \newcite{ganitkevitch2013ppdb}
addresses these issues of size and quality, but only for the limited
fragment of the NLI problem that is captured by paraphase.

@@

With our corpus, we sought to address the issues of size, quality, and
indeterminacy. To do this, we employed a crowdsourcing framework with
the following crucial innovations. First, the examples were grounded
in specific scenarios, and the premise and hypothesis sentences in each example 
were constrained to describe that scenario from the same perspective, 
which helps greatly in controlling event and entity coreference. Second, the prompt
gave participants the freedom to produce entirely novel sentences
within the task setting, which led to richer examples than we see with
the more proscribed string-editing techniques of earlier approaches,
without sacrificing consistency. Third, a subset of the resulting
sentences were sent to a validation task aimed at providing a highly 
reliable set of annotations over the same data, and at identifying areas of inferential uncertainty.

@@

In order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we performed an additional round of validation for about 10\% of our data.
This validation phase followed the same basic form as the Mechanical Turk labeling task used to label the SICK entailment data: we presented workers with pairs of sentences in batches of five, and asked them to choose a single label for each pair. We supplied each pair to four annotators, yielding five labels per pair including the label used by the original author. The instructions were similar to the instructions for initial data collection shown in \reffig{instructions-1}, and linked to a similar FAQ. Though we initially used a very restrictive qualification (based on past approval rate) to select workers for the validation task, we nonetheless discovered (and excluded from the corpus) some instances of random guessing in an early batch of work, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.

@@

The results of this validation process
are summarized in \reftab{validation-stats}. 
Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are very nearly evenly
distributed across the three labels. The Fleiss $\kappa$ scores 
(computed over every example with a full five annotations)
are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rate of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

The data will be released upon publication under a CreativeCommons
Attribution-ShareAlike license, the same licence used for the Flickr30k source captions.

### 2015-06-01 writing/SNLI paper/entailment_eval.tex
Updated classifier numbers
Tentative 3-class results
CP comments.

The most immediate application for our corpus is in developing models for the task of NLI. In particular, since it is dramatically larger than any existing corpus of comparable quality, we expect it to be suitable for training  parameter-rich models like neural networks for this task. In this section, we explore the performance of a range of standard and novel models trained on the corpus.

@@

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\textbf{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}  & \t{71.9} & \t{65.4} & \t{61.9} \\
\t{Classifier Based}     & \t{72.2} & \t{74.3} & \t{61.5} \\
%\midrule
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
Accuracies of two entailment algorithms included in the
  Excitement Open Platform.
Note that all accuracies are are on a 2-class
  classification task; this results in a majority-class baseline
  of 66\% on our class and 71\% on SICK.
%All RTE results are 2-class accuracy.
%The transformation based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

%In fact, the addition of these features alone allow the classifier to
%  outperform many of the .
%  This seems initially surprising, but it makes sense given how our corpus differs from existing ones:
%  the EOP systems have been tuned on relatively small corpora
%  ($\sim$1600 examples), whereas a classifier trained on our corpus can make use of
%  over two orders of magnitude more data.

@@

Our corpus is uniquely suitable for training neural network models that produce distributed representations of sentence meaning. In this section, we compare the performance of three such models on the corpus. 
To focus specifically on the strengths of these models at producing informative sentence representations, we use sentence embedding as an intermediate step in the NLI classification task: each model must produce a vector representation of each of the two sentences without using any context from the other sentence, and the two resulting vectors are then passed to a neural network classifier which predicts the label for the pair. This choice allows us to focus on existing models for sentence embedding, and it allows us to evaluate the ability of those models to learn useful representations of meaning (which may be independently useful for subsequent tasks), at the cost of excluding from consideration possible strong neural models for NLI that directly compare the two inputs at the word or phrase level.

@@

Our neural network classifier, depicted in \reffig{modelstructure}, is simply a stack of three 200d $\tanh$ layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the sentence embedding model itself.

We test three sentence embedding models, each set to use 100d phrase and sentence embeddings. Our baseline sentence embedding simply sums the embeddings of the words in each sentence. In addition, we experiment with two simple sequence embedding models models: a plain RNN and an LSTM RNN \cite{hochreiter1997long}. Both use the simple conventional layout with one layer per input token.

The word embeddings for all of the models are initialized with the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned as part of training. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each, and additionally applied dropout \cite{srivastava2014dropout} to the inputs and outputs of the sentence embedding models (though not to its internal connections) with a fixed dropout rate. All models were implemented in a common framework for this paper, and the implementations will be made available at publication time.

@@

\Fig{learning_curves_bow.pdf}{0.45}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers and the LSTM,
plotted on a log scale. The y axis starts at a random-chance accuracy of 33\%. The minibatch size of 64 that we used to tune the LSTM sets a lower bound on data for that model.}

@@

There are revealing patterns in the errors common to all the models
considered here. Despite the large size of the training corpus and the
distributional information captured by GloVe initialization, many
lexical relationships are still misanalyzed, leading to incorrect
predictions of \ii{independent}, even for pairs that are common in the
training corpus like \word{beach}/\word{surf} and
\word{sprinter}/\word{runner}. Semantic mistakes at the phrasal level
(e.g., predicting contradiction for word{A male is placing an order in a 
deli}/\word{A man buying a sandwich at a deli}) indicate
that additional attention to compositional semantics would pay off.
%
% Others that could replace the above:
% \word{Two teen girls relax on a black futon}/\word{Two young girls are sitting inside}
% \word{A male is placing an order in a deli}/\word{A man buying a sandwich at a deli}
% \word{A shopper buys cat food at a Walmart}/\word{A person shops for their pet at a store}
However, many of the persistent problems run deeper, to inferences
that depend on world knowledge and context-specific inferences, as in
the entailment pair \word{A race car driver leaps from a burning
  car}/\word{A race car driver escaping danger}, for which both
the lexicalized classifier and the LSTM predict \ii{neutral}. 
In other cases, models' attempts to shortcut this kind of inference 
through lexical cues can lead them astray. 
Some of these examples have qualities
reminiscent of Winograd schemas \cite{Winograd:1972,Levesque:2013}. For
example, all the models wrongly predict
entailment for \word{A young girl throws sand toward the
  ocean}/\word{A girl can't stand the ocean}, presumably because of
distributional associations between \word{throws} and \word{can't
  stand}.

Analysis of the models' predictions also yields insights into the
extent to which they grapple with event and entity coreference. For
the most part, the original image prompts contained a focal element
that the caption writer identified with a syntactic subject, following
information structuring conventions associating subjects and topics in
English \cite{Ward04}. Our annotators generally followed suit, writing
sentences with similar topic/focus (theme/rheme) structure that
promotes a coherent, situation-specific construal of each sentence
pair. This is information that our models can easily take advantage
of, but it can lead them astray. For instance, all of them stumble
with the amusingly simple case \emph{A woman prepares ingredients for
  a bowl of soup}/\emph{A soup bowl prepares a woman}, in which prior
expectations about parallelism are not met. Another headline example
of this type is \emph{A man wearing padded arm protection is being
  bitten by a German shepherd dog}/\emph{A man bit a dog}, which all
the models wrongly diagnose as \ii{entailment}, though the sentences
report two very different stories.

>>>>

% The most immediate application for our corpus is in developing models for the task of NLI. In particular, since it is dramatically larger than any existing corpus of comparable quality, we expect it to be suitable for training  parameter-rich models like neural networks for this task. In this section, we explore the performance of a range of standard and novel models trained on the corpus.

@@

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\textbf{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}        & \t{71.9} & \t{65.4} & \t{61.9} \\
\t{Classifier Based}           & \t{72.2} & \t{71.4} & \t{61.5} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
Accuracies for two entailment algorithms included in the
  Excitement Open Platform.
Note that all accuracies are are on a 2-class
  classification task; this results in a majority-class baseline
  of 66\% on our class and 71\% on SICK.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

%In fact, the addition of these features alone allow the classifier to
%  outperform many of the .
%  This seems initially surprising, but it makes sense given how our corpus differs from existing ones:
%  the EOP systems have been tuned on relatively small corpora
%  ($\approx$1600 examples), whereas a classifier trained on our corpus can make use of
%  over two orders of magnitude more data.

@@

Our corpus is suitably large and diverse to make it possible to train neural network models that produce distributed representations of sentence meaning. In this section, we compare the performance of three such models on the corpus. To focus specifically on the strengths of these models at producing informative sentence representations, we use sentence embedding as an intermediate step in the NLI classification task: each model must produce a vector representation of each of the two sentences without using any context from the other sentence, and the two resulting vectors are then passed to a neural network classifier which predicts the label for the pair. This choice allows us to focus on existing models for sentence embedding, and it allows us to evaluate the ability of those models to learn useful representations of meaning (which may be independently useful for subsequent tasks), at the cost of excluding from consideration possible strong neural models for NLI that directly compare the two inputs at the word or phrase level.

@@

Our neural network classifier, depicted in \reffig{modelstructure} (and based on a one-layer model in \citealt{Bowman:Potts:Manning:2014}), is simply a stack of three 200d $\tanh$ layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the sentence embedding model itself.

We test three sentence embedding models, each set to use 100d phrase and sentence embeddings. Our baseline sentence embedding simply sums the embeddings of the words in each sentence. In addition, we experiment with two simple sequence embedding models: a plain RNN and an LSTM RNN \cite{hochreiter1997long}. Both use the simple conventional layout with one layer per input token.

The word embeddings for all of the models are initialized with the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine-tuned as part of training. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each, and additionally applied dropout \cite{srivastava2014dropout} to the inputs and outputs of the sentence embedding models (though not to its internal connections) with a fixed dropout rate. All models were implemented in a common framework for this paper, and the implementations will be made available at publication time.

@@

\Fig{learning_curves_bow.pdf}{0.45}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers and the LSTM,
plotted on a log scale. The y-axis starts at a random-chance accuracy of 33\%. The minibatch size of 64 that we used to tune the LSTM sets a lower bound on data for that model.}

@@

There are revealing patterns in the errors common to all the models
considered here. Despite the large size of the training corpus and the
distributional information captured by GloVe initialization, many
lexical relationships are still misanalyzed, leading to incorrect
predictions of \ii{independent}, even for pairs that are common in the
training corpus like \word{beach}/\word{surf} and
\word{sprinter}/\word{runner}. Semantic mistakes at the phrasal level
(e.g., predicting contradiction for \word{A male is placing an order in a 
deli}/\word{A man buying a sandwich at a deli}) indicate
that additional attention to compositional semantics would pay off.
%
% Others that could replace the above:
% \word{Two teen girls relax on a black futon}/\word{Two young girls are sitting inside}
% \word{A male is placing an order in a deli}/\word{A man buying a sandwich at a deli}
% \word{A shopper buys cat food at a Walmart}/\word{A person shops for their pet at a store}
However, many of the persistent problems run deeper, to inferences
that depend on world knowledge and context-specific inferences, as in
the entailment pair \word{A race car driver leaps from a burning
  car}/\word{A race car driver escaping danger}, for which both
the lexicalized classifier and the LSTM predict \ii{neutral}. 
In other cases, the models' attempts to shortcut this kind of inference 
through lexical cues can lead them astray. 
Some of these examples have qualities
reminiscent of Winograd schemas \cite{Winograd:1972,Levesque:2013}. For
example, all the models wrongly predict
entailment for \word{A young girl throws sand toward the
  ocean}/\word{A girl can't stand the ocean}, presumably because of
distributional associations between \word{throws} and \word{can't
  stand}.

Analysis of the models' predictions also yields insights into the
extent to which they grapple with event and entity coreference. For
the most part, the original image prompts contained a focal element
that the caption writer identified with a syntactic subject, following
information structuring conventions associating subjects and topics in
English \cite{Ward04}. Our annotators generally followed suit, writing
sentences that, while structurally diverse, share topic/focus (theme/rheme)
structure with their premises.
This promotes a coherent, situation-specific construal of each sentence
pair. This is information that our models can easily take advantage
of, but it can lead them astray. For instance, all of them stumble
with the amusingly simple case \emph{A woman prepares ingredients for
  a bowl of soup}/\emph{A soup bowl prepares a woman}, in which prior
expectations about parallelism are not met. Another headline example
of this type is \emph{A man wearing padded arm protection is being
  bitten by a German shepherd dog}/\emph{A man bit a dog}, which all
the models wrongly diagnose as \ii{entailment}, though the sentences
report two very different stories.

### 2015-06-01 writing/SNLI paper/intro.tex
CP comments.

\begin{table*}[t]
  \centering\footnotesize
  \begin{tabular}{p{6.4cm}p{1.7cm}p{6.4cm}}
  \toprule
A man inspects the uniform of a figure in some East Asian country. & \fulllabel{contradiction}{c c c c c} & The man is sleeping\\
\rule{0pt}{3ex}An older and younger man smiling. & \fulllabel{neutral}{n n e n n} & Two men are smiling and laughing at the cats playing on the floor.\\
\rule{0pt}{3ex}A black race car starts up in front of a crowd of people. & \fulllabel{contradiction}{c c c c c} & A man is driving down a lonely road.\\
\rule{0pt}{3ex}A soccer game with multiple males playing. & \fulllabel{entailment}{e e e e e} & Some men are playing a sport.\\
\rule{0pt}{3ex}A smiling costumed woman is holding an umbrella. & \fulllabel{neutral}{n n e c n} & A happy woman in a fairy costume holds an umbrella.\\
    \bottomrule
% From 1.0rc3
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from the development section of our new corpus, shown with both the gold labels and the full set of annotator labels (abbreviated).}
\end{table*}

@@

NLI has been addressed using a variety of techniques, including
those based on symbolic logic, knowledge bases, and neural networks. 
In recent years, it has become an important testing ground for
approaches employing \emph{distributed} word and phrase
representations. Distributed representations excel at capturing
relations based in similarity, and they have proven effective at
modeling simple dimensions of meaning like evaluative sentiment
(e.g., \citealt{socher2013recursive}), but it is less clear that they can be
trained to support the full range of logical and commonsense
inferences required for NLI \cite{Weston-etal:2015,Weston-etal:2015Q}. 
In the SemEval 2014 entailment task, which was aimed at evaluating distributed
representations for NLI, the best-performing systems relied heavily on
additional features and reasoning capabilities
\cite{marelli2014semeval}.

@@

To address this, this paper introduces a new corpus of sentence pairs labeled for
entailment, contradiction, and semantic independence. At 570,152
sentence-pairs, this corpus is two orders of magnitude larger than all
other resources of its type. And, in contrast to many such resources,
all of the sentences were written by humans in a grounded,
naturalistic context. In a separate validation phase, we collected
four additional judgments for each label for 56,941 of the examples.
Of these, 98\% of cases emerge with a three-annotator consensus, 
and 58\% see a unanimous consensus from all five annotators.

>>>>

\begin{table*}[t]
  \centering\small
  \begin{tabular}{p{6.4cm}p{1.7cm}p{6.4cm}}
  \toprule
A man inspects the uniform of a figure in some East Asian country. & \fulllabel{contradiction}{c c c c c} & The man is sleeping\\
\rule{0pt}{3ex}An older and younger man smiling. & \fulllabel{neutral}{n n e n n} & Two men are smiling and laughing at the cats playing on the floor.\\
\rule{0pt}{3ex}A black race car starts up in front of a crowd of people. & \fulllabel{contradiction}{c c c c c} & A man is driving down a lonely road.\\
\rule{0pt}{3ex}A soccer game with multiple males playing. & \fulllabel{entailment}{e e e e e} & Some men are playing a sport.\\
\rule{0pt}{3ex}A smiling costumed woman is holding an umbrella. & \fulllabel{neutral}{n n e c n} & A happy woman in a fairy costume holds an umbrella.\\
    \bottomrule
% From 1.0rc3
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from the development section of our new corpus, shown with both the gold labels and the full set of annotator labels (abbreviated).}
\end{table*}

@@

NLI has been addressed using a variety of techniques, including
those based on symbolic logic, knowledge bases, and neural networks. 
In recent years, it has become an imp`ortant testing ground for
approaches employing \emph{distributed} word and phrase
representations. Distributed representations excel at capturing
relations based in similarity, and they have proven effective at
modeling simple dimensions of meaning like evaluative sentiment
(e.g., \citealt{socher2013recursive}), but it is less clear that they can be
trained to support the full range of logical and commonsense
inferences required for NLI \cite{Bowman:Potts:Manning:2014,Weston-etal:2015,Weston-etal:2015Q}. 
In the SemEval 2014 entailment task, which was aimed at evaluating distributed
representations for NLI, the best-performing systems relied heavily on
additional features and reasoning capabilities
\cite{marelli2014semeval}.

@@

To address this, this paper introduces a new corpus of sentence pairs labeled for
entailment, contradiction, and semantic independence. At 570,152
sentence pairs, this corpus is two orders of magnitude larger than all
other resources of its type. And, in contrast to many such resources,
all of the sentences were written by humans in a grounded,
naturalistic context. In a separate validation phase, we collected
four additional judgments for each label for 56,941 of the examples.
Of these, 98\% of cases emerge with a three-annotator consensus, 
and 58\% see a unanimous consensus from all five annotators.
